---
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Please run the following chunks before running the models  -->

```{r}
#| echo: false
## cargar base
library(tidyverse)
load("input/proc/micro-macro-merge.rdata")

datos_merge <- datos_merge |>
  mutate(across(where(haven::is.labelled), ~ vctrs::vec_data(.)),
         pais= as.factor(pais))

datos_merge$country_wave = do.call(paste, c(datos_merge[c("pais", "ola")], sep = "_"))
```

```{r data-fig-macro}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))    
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra,grid)  
rm(list=ls())

load("input/proc/micro-macro-merge.rdata")

datos_merge <- datos_merge |>
  mutate(across(where(haven::is.labelled), ~ vctrs::vec_data(.)),
         pais= as.factor(pais))

datos_merge$country_wave = do.call(paste, c(datos_merge[c("pais", "ola")], sep = "_"))

wid_data <- haven::read_dta(file = "input/proc/wid_data.dta")
wid_data <- wid_data %>% mutate(yr2=substr(year, 3, 4)) %>% rename(iso2c=country)
datos_merge$iso2c<- countrycode::countrycode(sourcevar = datos_merge$pais,origin = "country.name",destination = "iso2c")
wid_data$iso2c <- as.character(wid_data$iso2c)
datos_merge$yr2<- substr(datos_merge$ola, 3, 4)

frhouse <- read.csv("input/orig/freedom-score-fh.csv")
frhouse<- 
frhouse %>% select(country=Entity,iso3c=Code,year=Year,frhouse=Total.democracy.score) %>% 
  mutate(iso2c =countrycode::countrycode(sourcevar = iso3c,origin = "iso3c",destination = "iso2c")) %>% 
  mutate(yr2 = substr(year, 3, 4)) %>% 
  filter(iso2c %in% datos_merge$iso2c)
  
datos_merge<- 
left_join(x = datos_merge,y = wid_data[,c("iso2c","yr2","wid_gini_disp")],
          by =c("iso2c","yr2"))

datos_merge<- 
left_join(x = datos_merge,y = frhouse[,c("iso2c","yr2","frhouse")],
          by =c("iso2c","yr2"))

datos_macro <- datos_merge %>%
  mutate(
   cohesion_horizontal,
      cohesion_vertical,
      cohesion_general,
      gini_index,
      wid_gini_disp,  
      pib_per_capita_ppa,
      log_pib_per_capita_ppa,
      percent_pob_migrante,
      indice_v_dem,
      regulatory_quality,
      voice_and_accountability,
      wgi,
     frhouse, 
    edad_c = scale(edad) %>% as.numeric(),
    ola_s = as.numeric(scale(ola, center = TRUE, scale = TRUE)),
   income_decile,
    ola,
    nivel_educ   = forcats::fct_drop(factor(nivel_educ)),
    pos_politica = forcats::fct_drop(factor(pos_politica)),
    sexo         = forcats::fct_drop(factor(sexo)),
    pais         = forcats::fct_drop(factor(pais)),
    country_wave = forcats::fct_drop(factor(country_wave))
  ) %>% 
    select(cohesion_horizontal,
      cohesion_vertical,
      cohesion_general,
      gini_index,wid_gini_disp,
      pib_per_capita_ppa,
      log_pib_per_capita_ppa,
      percent_pob_migrante,
      indice_v_dem,
      regulatory_quality,
      voice_and_accountability,wgi,frhouse,
      income_decile,escolaridad,
         nivel_educ, sexo, edad_c, ola_s,ola, pos_politica,iso2c,
         country_wave, pais, wt)

# dim(datos_macro);dim(na.omit(datos_macro))
datos_macro$yr2<- substr(datos_macro$ola, 3, 4)

df_sum <- datos_macro %>%
  group_by(iso2c, yr2) %>%
  summarise(across(
    c(cohesion_horizontal,
      cohesion_vertical,
      cohesion_general,
      gini_index,wid_gini_disp,
      pib_per_capita_ppa,
      log_pib_per_capita_ppa,
      percent_pob_migrante,
      indice_v_dem,frhouse,
      wgi),
    mean,
    na.rm = TRUE
  )) %>%
  ungroup() 
df_sum <- 
 df_sum %>% 
  group_by(iso2c) %>%
  mutate(across(
    c(cohesion_horizontal,
      cohesion_vertical,
      cohesion_general,
      gini_index,wid_gini_disp,
      pib_per_capita_ppa,
      log_pib_per_capita_ppa,
      percent_pob_migrante,
      indice_v_dem,frhouse,
      wgi),
    mean,
    na.rm = TRUE,
    .names = "mid_{.col}"
  )) %>%
  ungroup()

df_sum$ctyear <- paste0(df_sum$iso2c,df_sum$yr2)
```

```{r data-model-fit}
#| label: preparacion-datos
#| eval: false

# Separar los efectos
datos_merge <- datos_merge |>
  group_by(pais) |>
 mutate(pib_be = mean(log_pib_per_capita_ppa, na.rm=T),
         # gini_be = mean(gini_index, na.rm=T),
         gini_be = mean(wid_gini_disp, na.rm=T),
         mig_be = mean(percent_pob_migrante, na.rm=T),
         dem_be = mean(indice_v_dem, na.rm=T),
         wgi_be = mean(wgi, na.rm=T),
         fho_be = mean(frhouse, na.rm=T),
         # edu_be = mean(edu_terciaria, na.rm=T)
        ) |>
  ungroup() |>
  mutate(pib_we = log_pib_per_capita_ppa - pib_be,
          # gini_we = gini_index - gini_be,
          gini_we = wid_gini_disp - gini_be,
          mig_we = percent_pob_migrante - mig_be,
          dem_we = indice_v_dem - dem_be,
          wgi_we = wgi- wgi_be,
          fho_we = frhouse- fho_be,
          # edu_we = edu_terciaria-edu_be
         )

# Centrado y limpieza

z <- function(x) as.numeric(scale(x))

datos_fit <- datos_merge %>%
  filter(!pais %in% c("Canada","United States","Trinidad & Tobago")) %>% 
  mutate(
    # pib_we  = z(pib_we),   gini_we = z(gini_we), wgi_we = z(wgi_we), dem_we = z(dem_we),
    # mig_we  = z(mig_we),   edu_we = z(edu_we),
    # pib_be  = z(pib_be),   gini_be = z(gini_be), wgi_be = z(wgi_be), dem_be = z(dem_be),
    # mig_be  = z(mig_be),   edu_be = z(edu_be),
    edad_c = scale(edad) %>% as.numeric(),
    ola_s = as.numeric(scale(ola, center = TRUE, scale = TRUE)),
    ola,
    nivel_educ   = forcats::fct_drop(factor(nivel_educ)),
    pos_politica = forcats::fct_drop(factor(pos_politica)),
    sexo         = forcats::fct_drop(factor(sexo)),
    pais         = forcats::fct_drop(factor(pais)),
    country_wave = forcats::fct_drop(factor(country_wave)),

    # --- cambiar categoría de referencia ---
    nivel_educ   = forcats::fct_relevel(nivel_educ, "Primary"),   # ejemplo
    pos_politica = forcats::fct_relevel(pos_politica, "Not declared")         # ejemplo
  ) |>
  select(cohesion_general_ind, cohesion_vertical_ind, cohesion_horizontal_ind,
         nivel_educ, sexo, edad_c, ola_s, pos_politica,ola,
         income_decile,escolaridad,
         pib_we, gini_we, dem_we, wgi_we, mig_we,fho_we,
         pib_be, gini_be, dem_be, wgi_be, mig_be,fho_be, 
         country_wave, pais, wt) 

save(datos_fit, file="input/proc/datos-fit.rdata")
```

# Resultados

## Análisis Factorial Confirmatorio

```{r fit-cfa}
#| eval: false
library(lavaan)
library(texreg)

# confianza_it_ind     = row_mean_if_complete(cur_data(), c("it1"), 1L),
# seguridad_ind        = row_mean_if_complete(cur_data(), c("aoj11","vic1ext"), 2L),
# confianza_inst_ind   = row_mean_if_complete(cur_data(), c("b13","b21","b31"), 2L),  
# democracia_ind       = row_mean_if_complete(cur_data(), c("ing4","pn4"), 2L)        
load("input/proc/micro-macro-merge.rdata")

m1 <- '
seguridad_ind =~ aoj11+vic1ext
# confianza_it_ind =~ it1
confianza_inst_ind =~ b13+b21+b31
democracia_ind =~ ing4+pn4

ch =~ seguridad_ind + it1
cv =~ confianza_inst_ind + democracia_ind
cg =~ ch+ cv
'
m1_cfa <- cfa(m1, data = datos_merge[,c("aoj11","vic1ext","it1","b13","b21","b31","ing4","pn4","pais")],cluster = "pais")
screenreg(m1_cfa)
semPlot::semPaths(m1_cfa,what = "std")
fitmeasures(m1_cfa, fit.measures = c("rmsea", "cfi", "chisq", "pvalue", "df"))
# save(m1_cfa, file="output/cfa.rdata")
```

```{r}
#| label: fig-afc
#| fig-width: 10
#| fig-height: 5
#| fig-cap: Análisis Factorial Confirmatorio Modelo de Medición de Cohesión Social
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))  

library(semPlot)
library(tidySEM)
library(lavaan)
library(ggplot2)

m1 <- '
  ch =~ seguridad_ind + confianza_it_ind
  cv =~ confianza_inst_ind + democracia_ind
'

datos_merge <- datos_merge %>% filter(!pais %in% c("Canada","United States","Trinidad & Tobago"))
m1_cfa <- cfa(m1, data = datos_merge)
# summary(m1_cfa, standardized = TRUE, fit.measures = TRUE)

fit <- fitmeasures(m1_cfa, fit.measures = c("rmsea", "cfi", "chisq", "pvalue", "df"))

# ?graph_sem(m1_cfa)

fit_edges<- get_edges(m1_cfa)
fit_edges$label <- fit_edges$est_sig_std

fit_nodes<- get_nodes(m1_cfa)
fit_nodes$label <- c("Horizontal","Vertical",
                     "Security","Interpersonal\nTrust",
                     "Institutional\nTrust","Democracy")

fit_layout<- get_layout("","ch","",  "","cv"," ",
                  "confianza_it_ind","","seguridad_ind",
                  "democracia_ind","","confianza_inst_ind", rows = 2)


fit_layout<- get_layout("confianza_it_ind","","", "democracia_ind",
                        "","ch","cv","",
                        "seguridad_ind" ,"","", "confianza_inst_ind", rows = 3)

fit_nodes$label_size = 4
fit_nodes$label_family = "serif"
graph_sem(m1_cfa,edges = fit_edges,layout=fit_layout,nodes=fit_nodes) + 
  labs(caption = paste0(
  "Note: RMSEA = ", round(fit["rmsea"], 3),
  ", CFI = ", round(fit["cfi"], 3),
  ", χ² = ", round(fit["chisq"], 2),
  ", df = ", fit["df"],
  ", p-value = ", format(round(fit["pvalue"], 4), nsmall = 3),
  ", N = ",format(nobs(m1_cfa), big.mark = ",", scientific = FALSE)
))

```

En @fig-afc se presentan los resultados del análisis factorial confirmatorio hecho a partir del modelo de medición propuesto. En primer lugar, se observa que los indicadores presentan cargas factoriales moderadas, las cuales van del 0.45 al 0.6 dependiendo del caso, lo que sugiere que los indicadores reflejan parcialmente las dimensiones latentes. Los índices de ajuste son de buena calidad, apuntando a una fiabilidad del constructo. Ahora, dado que el modelo cuenta con un solo grado de libertad, las medidas de ajuste global deben interpretarse con precaución. En suma, el modelo ofrece un ajuste aceptable a nivel identificacional, pero la validez de los factores son limitadas, lo que podría solucionarse aumentando el número o la calidad de los indicadores en futuras mediciones.


## Descriptives


```{r}
#| label: fig-cs
#| fig-cap: Evolución dimensiones Cohesión Social (2004-2022)
olas <- datos_merge |>
  group_by(ola) |>
  summarise(horizontal_prom = mean(`cohesion_horizontal_ind`, na.rm=T),
            vertical_prom = mean(`cohesion_vertical_ind`, na.rm=T),
            cohesion_prom = mean(`cohesion_general_ind`, na.rm=T)) |>
  pivot_longer(
    cols = c(horizontal_prom, vertical_prom, cohesion_prom),
    names_to = "indicador",
    values_to = "promedio"
  ) |>
  mutate(indicador = dplyr::recode(indicador,
                            horizontal_prom = "Horizontal Cohesion",
                            vertical_prom = "Vertical Cohesion",
                            cohesion_prom = "General Cohesion"))

olas$ola <- factor(olas$ola)
plot_cs <- olas |>
  ggplot(aes(x = ola, y = promedio, color = indicador,group = indicador)) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_y_continuous(limits = c(2,8))+
  labs(x = "Wave", y = "Social cohesion (1-10)", color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")

plot_cs
```

@fig-cs shows the averages for each year for the different types of cohesion. First, it can be seen that horizontal cohesion maintained an upward trend between 2004 and 2012, except for the decline in 2010. After this, horizontal cohesion faced a sustained decline until 2018, before rebounding and even exceeding its 2004 level. Vertical cohesion shows a similar pattern of variation to horizontal cohesion, with a persistent rise over time until 2012, when it suffered a sharp decline at the regional level. This decline continued until 2016, when the trend reversed, with an increase in vertical cohesion until the last year recorded. Although the latest measurement of vertical cohesion shows higher levels than at the beginning, its scores are generally considerably low when compared to horizontal cohesion, differing by approximately 1.5 points in all waves. In summary, Latin America has consistently shown greater horizontal cohesion than vertical cohesion from 2004 to 2022[^3]. 

[^3]: It should be noted that social cohesion (green line) is the average of vertical and horizontal cohesion, which is why its interpretation is not detailed.


## Relationship between and within country level factors with social cohesión

```{r fig-macro}
#| fig-width: 12
#| fig-height: 22
#| fig-cap: "Country-level association of macro-level factors and social cohesion. Red line represents the association including Canada and United States."
#| cache: true
library(ggrepel)

df_sum_la <-  df_sum %>% filter(!iso2c %in% c("US","CA"))
df_sum <- df_sum %>% filter(!iso2c=="TT")

fig_gini_h <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE,
              aes(mid_wid_gini_disp, y = mid_cohesion_horizontal),
              color = "red",size=0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE,
              aes(mid_wid_gini_disp, y = mid_cohesion_horizontal,fullrange=T),
              color = "black",fullrange=T) +
  geom_smooth(data = df_sum,
              aes(x = wid_gini_disp, y = cohesion_horizontal, color = iso2c, shape = iso2c),
              method = "lm", se = FALSE, color = "black",size=0.1) +
  geom_label(data = df_sum, aes(x = mid_wid_gini_disp, y = mid_cohesion_horizontal, label = iso2c),size=2.5) +
  scale_y_continuous(limits = c(2,8))+  
  labs(x = "Economic Inequality", y = " ", title = "Horizontal Cohesion") +
  annotate("label",
           x = Inf, y = -Inf,               
           hjust = 1.08, vjust = -1,      
           label = paste0("r = ", round(cor(df_sum$mid_wid_gini_disp,df_sum$mid_cohesion_horizontal,use = "complete.obs"), 2)),
           fill = "white",                 
           color = "red",                
           label.size = 0.25,family = "serif",
           size = 3.5)+
  annotate("label",
           x = Inf, y = -Inf,               
           hjust = 1.08, vjust = -3,      
           label = paste0("r = ", round(cor(df_sum_la$mid_wid_gini_disp,df_sum_la$mid_cohesion_horizontal,use = "complete.obs"), 2)),
           fill = "white",                 
           color = "black",                
           label.size = 0.25,family = "serif",
           size = 3.5) 

fig_gdp_h <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE,
              aes(mid_pib_per_capita_ppa, y = mid_cohesion_horizontal),
              color = "red", size = 0.5,fullrange = TRUE) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_pib_per_capita_ppa, y = mid_cohesion_horizontal),
              color = "black") +
  geom_smooth(data = df_sum,
              aes(x = pib_per_capita_ppa,
                  y = cohesion_horizontal,
                  color = iso2c,
                  shape = iso2c),
              method = "lm", se = FALSE,
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_pib_per_capita_ppa,
                 y = mid_cohesion_horizontal,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "GDP per Capita (PPP)", y = " ", title = "") +
  annotate("label",
           x = Inf, y = -Inf,
           hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_pib_per_capita_ppa,
                                    df_sum$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label",
           x = Inf, y = -Inf,
           hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_pib_per_capita_ppa,
                                    df_sum_la$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)


fig_mig_h <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_percent_pob_migrante, y = mid_cohesion_horizontal),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_percent_pob_migrante, y = mid_cohesion_horizontal),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = percent_pob_migrante, y = cohesion_horizontal,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_percent_pob_migrante,
                 y = mid_cohesion_horizontal,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "Migrant Population (%)", y = " ", title = "") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_percent_pob_migrante,
                                    df_sum$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_percent_pob_migrante,
                                    df_sum_la$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)


fig_vdem_h <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_indice_v_dem, y = mid_cohesion_horizontal),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_indice_v_dem, y = mid_cohesion_horizontal),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = indice_v_dem, y = cohesion_horizontal,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_indice_v_dem,
                 y = mid_cohesion_horizontal,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "Democracy", y = " ", title = "") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_indice_v_dem,
                                    df_sum$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_indice_v_dem,
                                    df_sum_la$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)


fig_wdi_h <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_wgi, y = mid_cohesion_horizontal),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_wgi, y = mid_cohesion_horizontal),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = wgi, y = cohesion_horizontal,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_wgi,
                 y = mid_cohesion_horizontal,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "Governance", y = " ", title = "") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_wgi,
                                    df_sum$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_wgi,
                                    df_sum_la$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)

fig_gini_v <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_wid_gini_disp, y = mid_cohesion_vertical),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_wid_gini_disp, y = mid_cohesion_vertical),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = wid_gini_disp, y = cohesion_vertical,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_wid_gini_disp,
                 y = mid_cohesion_vertical,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "Economic Inequality", y = " ", title = "Vertical cohesion") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_wid_gini_disp,
                                    df_sum$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_wid_gini_disp,
                                    df_sum_la$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)


fig_gdp_v <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_pib_per_capita_ppa, y = mid_cohesion_vertical),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_pib_per_capita_ppa, y = mid_cohesion_vertical),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = pib_per_capita_ppa, y = cohesion_vertical,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_pib_per_capita_ppa,
                 y = mid_cohesion_vertical,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "GDP per Capita (PPP)", y = " ", title = "") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_pib_per_capita_ppa,
                                    df_sum$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_pib_per_capita_ppa,
                                    df_sum_la$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)



fig_mig_v <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_percent_pob_migrante, y = mid_cohesion_vertical),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_percent_pob_migrante, y = mid_cohesion_vertical),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = percent_pob_migrante, y = cohesion_vertical,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_percent_pob_migrante,
                 y = mid_cohesion_vertical,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "Migrant Population (%)", y = " ", title = "") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_percent_pob_migrante,
                                    df_sum$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_percent_pob_migrante,
                                    df_sum_la$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)
  

fig_vdem_v <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_indice_v_dem, y = mid_cohesion_vertical),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_indice_v_dem, y = mid_cohesion_vertical),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = indice_v_dem, y = cohesion_vertical,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_indice_v_dem,
                 y = mid_cohesion_vertical,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "Democracy", y = " ", title = "") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_indice_v_dem,
                                    df_sum$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_indice_v_dem,
                                    df_sum_la$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)


fig_wdi_v <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_wgi, y = mid_cohesion_vertical),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_wgi, y = mid_cohesion_vertical),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = wgi, y = cohesion_vertical,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_wgi,
                 y = mid_cohesion_vertical,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "Governance", y = " ", title = "") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_wgi,
                                    df_sum$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -2,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_wgi,
                                    df_sum_la$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)


set.seed(1234)

grid.arrange(fig_gini_h,fig_gini_v,
             fig_gdp_h,fig_gdp_v,
             fig_vdem_h,fig_vdem_v,
             # fig_fho_v,fig_fho_h,
             fig_wdi_h,fig_wdi_v,
             fig_mig_h,fig_mig_v,
             nrow = 5, ncol=2,
 bottom =textGrob("Source: LAPOP (2004-2023); descriptive statistics; figure report country level pearson correlation; the line is the fitted values; CI at 95%",
 gp = gpar(fontface = 1, fontsize = 9),hjust = 1,x = 1
  ))
```

## Differences and changes in country level factors and social cohesión

```{r}
#| eval: false
load("input/proc/datos-fit.rdata")
m0_ch = lmer(cohesion_horizontal_ind ~ 1 + (1 | country_wave) + (1 |pais), data=datos_fit, weights=wt)
icc(m0_ch, by_group=TRUE) # 2.3% y 5.6%
m0_cv = lmer(cohesion_vertical_ind ~ 1 + (1 | country_wave) + (1 |pais), data=datos_fit, weights=wt)
icc(m0_cv, by_group=TRUE) # 6.3% y 6.3%
m0_cs = lmer(cohesion_general_ind ~ 1 + (1 | country_wave) + (1 |pais), data=datos_fit, weights=wt)
icc(m0_cs, by_group=TRUE) # 4.9% y 7.5%
save(m0_ch, file="output/modelo_nulo_horizontal.rdata")
save(m0_cv, file="output/modelo_nulo_vertical.rdata")
save(m0_cs, file= "output/modelo_nulo_completo.rdata")
```

```{r tbl-modelos-cohesion-micro}
#| label: tbl-modelos-cohesion-micro
#| results: asis
#| cache: true
#| tbl-cap: Multilevel regression for individual level factors and social cohesion
load("input/proc/datos-fit.rdata")
library(lme4)
library(texreg)
library(dplyr)

isced_labels <- c(
  "Early education/none",
  "Primary",
  "Lower secondary",
  "Upper secondary",
  "Postsecondary non-terciary",
  "Terciary (short-cycle)",
  "Universitary"
)

datos_fit$isced11 <- car::recode(datos_fit$escolaridad, 
"0 = 0;1:6 = 1;7:9 = 2;10:12 = 3;13:14 = 4;15:16 = 5;17:18 = 6")

datos_fit$isced11 <- factor(
  datos_fit$isced11,
  levels = 0:6,
  labels = isced_labels
)


datos_fit <- 
datos_fit %>% 
  select(cohesion_general_ind, cohesion_vertical_ind, cohesion_horizontal_ind,
         nivel_educ, sexo, edad_c, ola_s, pos_politica,ola,
         income_decile,isced11,escolaridad,
         pib_we, gini_we, dem_we, wgi_we, mig_we,fho_we,
         pib_be, gini_be, dem_be, wgi_be, mig_be,fho_be, 
         country_wave, pais, wt) %>% na.omit() %>% 
  filter(!pais %in% c("Canada","United States"))


micro_h2 <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) +  ola +  (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
micro_h <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola +  (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)

micro_v2 <- lmer(cohesion_vertical_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) +  ola +  (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
micro_v <- lmer(cohesion_vertical_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola +  (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)

coef_names<- list("(Intercept)"="(Intercept)",
"income_decile" ="Income decile",                  
# "nivel_educSecondary" = "Secondary", 
# "nivel_educTertiary" = "Tertiary",  
"isced11Primary"="Primary",                        
"isced11Lower secondary"="Lower secondary",                
"isced11Upper secondary"="Upper secondary",
"isced11Postsecondary non-terciary"="Postsecondary non-terciary",     
"isced11Terciary (short-cycle)"="Terciary (short-cycle)",         
"isced11Universitary"="Universitary",                   
"pos_politicaLeft"="Left",    
"pos_politicaCenter"="Center",  
"pos_politicaRight"="Right",
# ola2006 = "2006",
# ola2008 = "2008",
# ola2010 = "2010",
# ola2012 = "2012",
# ola2014 = "2014",
# ola2016 = "2016",
# ola2018 = "2018",
# ola2023 = "2023"
"ola"="Time",
"sexoMale"="Male (ref.=Female)",            
"edad_c"="Age",              
"I(edad_c^2)"="Age2"
)   

# knitreg(c(micro_h2,micro_h,micro_v2,micro_v),       # file = "output/table000.html",
#         custom.coef.map = coef_names,
#        groups = 
#          list("Education (ref.=No formal schooling)"=3:8,
#               "Political position (ref.=Undefined)"=9:11
#               # "Time trend (ref.=2004)"=10:17
#               ))

htmlreg(c(micro_h2,micro_h,micro_v2,micro_v),single.row = F,digits = 3,caption = NULL,
       # file = "output/table000.html",
        custom.coef.map = coef_names,
       groups = 
         list("Education (ref.=No formal schooling)"=3:8,
              "Political position (ref.=Undefined)"=9:11
              # "Time trend (ref.=2004)"=10:17
              ),
       custom.header = list("Horizontal"=2,"Vertical"=4),
       custom.gof.rows = list("Controls"=c(rep("Yes",4))),include.loglik = FALSE,include.aic = FALSE,
       custom.gof.names = c(NA,NA,"Num. Country-wave","Num. Country","Var: Country-wave (Intercept)","Var: Country (Intercept)","Var: Residual")
)
```

```{r}
#| fig-width: 10
#| fig-height: 5
#| eval: true
library(marginaleffects)
library(ggplot2)
p1 <- plot_predictions(model = micro_h,condition = "isced11") + 
  xlab("Education")+ylab("Horizontal Cohesion")

# p2 <- plot_predictions(model = micro_h2,condition = "escolaridad") + 
#   xlab("Year of Education")+ylab("Horizontal Cohesion")+
#   scale_y_continuous(limits = c(5,6))

p3 <- plot_predictions(model = micro_v,condition = "isced11") +
  xlab("Education")+ylab("Vertical Cohesion")

# p4 <- plot_predictions(model = micro_v,condition = "isced11") + 
#   xlab("Year of Education")+ylab("Vertical Cohesion")

grid.arrange(p1,p3)
```


```{r modelo-cohesion-full}
#| cache: true
#| results: asis
load("input/proc/datos-fit.rdata")
library(lme4)
library(texreg)
library(dplyr)
library(correlation)

isced_labels <- c(
  "Early education/none",
  "Primary",
  "Lower secondary",
  "Upper secondary",
  "Postsecondary non-terciary",
  "Terciary (short-cycle)",
  "Universitary"
)

datos_fit$isced11 <- car::recode(datos_fit$escolaridad, 
"0 = 0;1:6 = 1;7:9 = 2;10:12 = 3;13:14 = 4;15:16 = 5;17:18 = 6")

datos_fit$isced11 <- factor(
  datos_fit$isced11,
  levels = 0:6,
  labels = isced_labels
)


datos_fit <- 
datos_fit %>% 
  select(cohesion_general_ind, cohesion_vertical_ind, cohesion_horizontal_ind,
         nivel_educ, sexo, edad_c, ola_s, pos_politica,ola,
         income_decile,isced11,escolaridad,
         pib_we, gini_we, dem_we, wgi_we, mig_we,fho_we,
         pib_be, gini_be, dem_be, wgi_be, mig_be,fho_be, 
         country_wave, pais, wt) %>% na.omit() %>% 
  filter(!pais %in% c("Canada","United States"))

# datos_fit$dem_be <- datos_fit$fho_be
# datos_fit$dem_we <- datos_fit$fho_we

coef_names <- list(
  ola = "Time",
  gini_be = "Gini (BE)",
  gini_we = "Gini (WE)",
  pib_be = "GDP (BE)",
  pib_we = "GDP (WE)",
  dem_be = "Democracy (BE)",
  dem_we = "Democracy (WE)",
  wgi_be = "Governace (BE)",
  wgi_we = "Governace (WE)",
  mig_be = "Migration (BE)",
  mig_we = "Migration (WE)"
)

# corr_macro <- 
#   correlation::correlation(
#     dplyr::select(datos_fit,gini_be,gini_we,pib_be,pib_we,dem_be,dem_we,wgi_be,wgi_we,mig_be,mig_we)) 
# 
# display(summary(corr_macro),digits = 3,format = "markdown")

micro <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_econ <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we)
macro_econ_polit <- update(macro_econ,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we)
# macro_dem <- update(micro,. ~ . + mig_be+mig_we)
# macro_econ_dem <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we+mig_be+mig_we)
macro_econ_polit_dem <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we+mig_be+mig_we)

h_demo <- list(macro_econ,macro_econ_polit,macro_econ_polit_dem)
# screenreg(h_demo,digits=3,custom.coef.map = coef_names)

micro <- lmer(cohesion_vertical_ind ~ 1 + income_decile+ isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_econ <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we)
macro_econ_polit <- update(macro_econ,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we)
# macro_dem <- update(micro,. ~ . + mig_be+mig_we)
# macro_econ_dem <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we+mig_be+mig_we)
macro_econ_polit_dem <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we+mig_be+mig_we)

v_demo <- list(macro_econ,macro_econ_polit,macro_econ_polit_dem)

# screenreg(v_demo,digits=3,custom.coef.map = coef_names)

micro <- lmer(cohesion_general_ind ~ 1 + income_decile +isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_econ <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we)
macro_econ_polit <- update(macro_econ,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we)
# macro_dem <- update(micro,. ~ . + mig_be+mig_we)
# macro_econ_dem <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we+mig_be+mig_we)
macro_econ_polit_dem <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we+mig_be+mig_we)

g_demo <- list(macro_econ,macro_econ_polit,macro_econ_polit_dem) 
# screenreg(g_demo,digits=3,custom.coef.map = coef_names)
```

Table 4...

```{r}
#| label: tbl-table004
#| results: asis
#| cache: false
#| tbl-cap: Multilevel regression for macro factors and horizontal social cohesion
 
htmlreg(h_demo, digits=3,custom.coef.map = coef_names,caption = NULL,
        # file = "output/table004.html"
        )
```


Table 5...

```{r}
#| label: tbl-table005
#| results: asis
#| cache: false
#| tbl-cap: Multilevel regression for macro factors and vertical social cohesion

 
htmlreg(v_demo, digits=3,custom.coef.map = coef_names,caption = NULL,
        # file = "output/table005.html"
        )
```

Table 6...

```{r}
#| label: tbl-table006
#| results: asis
#| cache: false
#| tbl-cap: Multilevel regression for macro factors and general social cohesion
 
htmlreg(g_demo, digits=3,custom.coef.map = coef_names,caption = NULL,
        # file = "output/table006.html"
        )
```

# Interactions Interaciones de wave*macro_variable

```{r modelo-cohesion-int}
#| cache: true
#| results: asis
#| eval: true
load("input/proc/datos-fit.rdata")
library(lme4)
library(texreg)
library(dplyr)
library(correlation)
isced_labels <- c(
  "Early education/none",
  "Primary",
  "Lower secondary",
  "Upper secondary",
  "Postsecondary non-terciary",
  "Terciary (short-cycle)",
  "Universitary"
)

datos_fit$isced11 <- car::recode(datos_fit$escolaridad, 
"0 = 0;1:6 = 1;7:9 = 2;10:12 = 3;13:14 = 4;15:16 = 5;17:18 = 6")

datos_fit$isced11 <- factor(
  datos_fit$isced11,
  levels = 0:6,
  labels = isced_labels
)
datos_fit <- 
datos_fit %>% 
  select(cohesion_general_ind, cohesion_vertical_ind, cohesion_horizontal_ind,
         nivel_educ, sexo, edad_c, ola_s, pos_politica,ola,
         income_decile,isced11,escolaridad,
         pib_we, gini_we, dem_we, wgi_we, mig_we,fho_we,
         pib_be, gini_be, dem_be, wgi_be, mig_be,fho_be, 
         country_wave, pais, wt) %>% na.omit() %>% 
  filter(!pais %in% c("Canada","United States"))

# datos_fit$dem_be <- datos_fit$fho_be
# datos_fit$dem_we <- datos_fit$fho_we

coef_names <- list(
  ola = "Time",
  gini_be = "Gini (BE)",
  gini_we = "Gini (WE)",
  pib_be = "GDP (BE)",
  pib_we = "GDP (WE)",
  dem_be = "Democracy (BE)",
  dem_we = "Democracy (WE)",
  wgi_be = "Governace (BE)",
  wgi_we = "Governace (WE)",
  mig_be = "Migration (BE)",
  mig_we = "Migration (WE)"
)

hz_1 <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola +  gini_be*ola+gini_we*ola+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we+mig_be+mig_we+(1 | country_wave) + (ola| pais), data= datos_fit, weights= wt)
hz_2 <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola +  gini_be+gini_we+pib_be+pib_we+dem_be*ola+dem_we*ola+wgi_be+wgi_we +mig_be+mig_we+(1 | country_wave) + (ola| pais), data= datos_fit, weights= wt)
hz_3 <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola +  gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be*ola+wgi_we*ola+mig_be+mig_we+(1 | country_wave) + (ola| pais), data= datos_fit, weights= wt)
hz_4 <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola +  gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we+mig_be*ola+mig_we*ola+(1 | country_wave) + (ola| pais), data= datos_fit, weights= wt)

hz_ola <- list(hz_1,hz_2,hz_3,hz_4)
# screenreg(hz_ola,digits=3)
htmlreg(hz_ola,digits=3)
vt_1 <- update(hz_1,cohesion_vertical_ind ~ . )
vt_2 <- update(hz_2,cohesion_vertical_ind ~ . )  
vt_3 <- update(hz_3,cohesion_vertical_ind ~ . ) #ola:wgi_we =  -0.144 *
vt_4 <- update(hz_4,cohesion_vertical_ind ~ . )

vt_ola <- list(vt_1,vt_2,vt_3,vt_4)
# screenreg(vt_ola,digits=3)
htmlreg(vt_ola,digits=3)

cg_1 <- update(hz_1,cohesion_general_ind ~ . )
cg_2 <- update(hz_2,cohesion_general_ind ~ . )  
cg_3 <- update(hz_3,cohesion_general_ind ~ . ) # #ola:wgi_we =  -0.100 *
cg_4 <- update(hz_4,cohesion_general_ind ~ . )

cg_ola <- list(cg_1,cg_2,cg_3,cg_4)
# screenreg(cg_ola,digits=3)
htmlreg(cg_ola,digits=3)
```


Así...

```{r}
#| label: tbl-modelos-cohesion
#| results: asis
#| echo: false
#| eval: false
#| cache: true
load("input/proc/datos-fit.rdata")
library(lme4)
library(texreg)
library(dplyr)

# datos_fit$ola<- factor(datos_fit$ola)
datos_fit_la <- datos_fit %>% filter(!pais %in% c("Canada","United States"))
# Socioeconomic dimensions------------------------------------------------------
micro <- lmer(cohesion_horizontal_ind ~ 1 + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_gini <- update(micro,. ~ . + gini_be + gini_we)
macro_gdp <- update(micro,. ~ . + pib_be + pib_we)
macro_econ <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we)
# macro_econ_la_h <- update(macro_econ,data=datos_fit_la) #using only LATAM
h_econ <- list(macro_gini,macro_gdp,macro_econ)

micro <- lmer(cohesion_vertical_ind ~ 1 + isced11 + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_gini <- update(micro,. ~ . + gini_be + gini_we)
macro_gdp <- update(micro,. ~ . + pib_be + pib_we)
macro_econ <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we)
# macro_econ_la_v <- update(macro_econ,data=datos_fit_la) #using only LATAM
v_econ <- list(macro_gini,macro_gdp,macro_econ)

# screenreg(c(h_econ,v_econ))

htmlreg(c(h_econ,v_econ),single.row = F,digits = 3,
       # file = "output/table001.html",
        caption.above = T,
        caption = "Multilevel regression for socioeconomic macro factors and social cohesion", 
          custom.coef.map = 
            list(
              gini_be ="Gini (BE)",
              gini_we ="Gini (WE)",
              pib_be = "GDP (BE)", 
              pib_we = "GDP (WE)",
              # ola2006 = "Time (ref.= 2004) 2006",
              # ola2008 = "2008",
              # ola2010 = "2010",
              # ola2012 = "2012",
              # ola2014 = "2014",
              # ola2016 = "2016",
              # ola2018 = "2018",
              # ola2023 = "2023"   
              ola = "Time"              
            ),custom.header = list("Horizontal"=1:3,"Vertical"=4:6),
          custom.gof.rows = 
            list(Controls=c("Yes","Yes","Yes","Yes","Yes","Yes"))
          )

# Political dimensions------------------------------------------------------
micro <- lmer(cohesion_horizontal_ind ~ 1 + nivel_educ + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_dem <- update(micro,. ~ . + dem_be + dem_we)
macro_wgi <- update(micro,. ~ . + wgi_be + wgi_we)
macro_pol <- update(micro,. ~ . + dem_be+dem_we+wgi_be + wgi_we)
# macro_pol_la_v <- update(macro_pol,data=datos_fit_la) #using only LATAM
h_pol <- list(macro_dem,macro_wgi,macro_pol)

micro <- lmer(cohesion_vertical_ind ~ 1 + nivel_educ + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_dem  <- update(micro,. ~ . + dem_be + dem_we)
macro_wgi <- update(micro,. ~ . + wgi_be + wgi_we)
macro_pol  <- update(micro,. ~ . + dem_be+dem_we+wgi_be + wgi_we)
# macro_pol_la_h <- update(macro_pol,data=datos_fit_la) #using only LATAM

v_pol <- list(macro_dem,macro_wgi,macro_pol)

#screenreg(c(h_pol,v_pol))
htmlreg(c(h_pol,v_pol),single.row = F,digits = 3,
        # file = "output/table002.html",
        caption.above = T,
        caption = "Multilevel regression for institutional macro factors and social cohesion", 
          custom.coef.map = 
            list(
              dem_be ="Democracy (BE)",
              dem_we ="Democracy (WE)",
              wgi_be = "Governace (BE)", 
              wgi_we = "Governace (WE)",
              # ola2006 = "Time (ref.= 2004) 2006",
              # ola2008 = "2008",
              # ola2010 = "2010",
              # ola2012 = "2012",
              # ola2014 = "2014",
              # ola2016 = "2016",
              # ola2018 = "2018",
              # ola2023 = "2023"
              ola = "Time"
            ),custom.header = list("Horizontal"=1:3,"Vertical"=4:6),
          custom.gof.rows = 
            list(Controls=c("Yes","Yes","Yes","Yes","Yes","Yes"))          
          )

# Demographic ------------------------------------------------------------------
micro <- lmer(cohesion_horizontal_ind ~ 1 + nivel_educ + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_mig <- update(micro,. ~ . + mig_be + mig_we)
# macro_mig_time <- update(micro,. ~ . + mig_be*ola + mig_we*ola)
h_demo <- list(macro_mig)

micro <- lmer(cohesion_vertical_ind ~ 1 + nivel_educ + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_mig <- update(micro,. ~ . + mig_be + mig_we)
# macro_mig_time <- update(micro,. ~ . + mig_be*ola + mig_we*ola)
v_demo <- list(macro_mig)

#screenreg(c(h_demo,v_demo))
htmlreg(c(h_demo,v_demo),single.row = F,digits = 3,
        # file = "output/table003.html",
        caption.above = T,
        caption = "Multilevel regression for demographic macro factors and social cohesion", 
          custom.coef.map = 
            list(mig_be ="Migration (BE)",
                 mig_we = "Migration (WE)",
              # ola2006 = "Time (ref.= 2004) 2006",
              # ola2008 = "2008",
              # ola2010 = "2010",
              # ola2012 = "2012",
              # ola2014 = "2014",
              # ola2016 = "2016",
              # ola2018 = "2018",
              # ola2023 = "2023"
              ola = "Time"
              ),
          ,custom.header = list("Horizontal"=1,"Vertical"=2),
          custom.gof.rows = 
            list(Controls=c("Yes","Yes"))          
          )
```


