

# Results {data-background-color="#1b241f"}

```{r}
#| echo: false
#| label: cargar-base
library(tidyverse)
library(lme4)
library(texreg)
library(dplyr)
library(haven)
library(correlation)
library(ggtext)
library(lavaan)
library(performance)

load("../../input/proc/micro-macro-merge.rdata")

datos_merge <- datos_merge |>
  mutate(across(where(haven::is.labelled), ~ vctrs::vec_data(.)),
         pais= as.factor(pais))

datos_merge$country_wave = do.call(paste, c(datos_merge[c("pais", "ola")], sep = "_"))
```

```{r data-fig-macro}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))    
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra,grid)  
rm(list=ls())

load("../../input/proc/micro-macro-merge.rdata")

datos_merge <- datos_merge |>
  mutate(across(where(haven::is.labelled), ~ vctrs::vec_data(.)),
         pais= as.factor(pais))

datos_merge$country_wave = do.call(paste, c(datos_merge[c("pais", "ola")], sep = "_"))

wid_data <- haven::read_dta(file = "../../input/proc/wid_data.dta")
wid_data <- wid_data %>% mutate(yr2=substr(year, 3, 4)) %>% rename(iso2c=country)
datos_merge$iso2c<- countrycode::countrycode(sourcevar = datos_merge$pais,origin = "country.name",destination = "iso2c")
wid_data$iso2c <- as.character(wid_data$iso2c)
datos_merge$yr2<- substr(datos_merge$ola, 3, 4)

frhouse <- read.csv("../../input/orig/freedom-score-fh.csv")
frhouse<- 
frhouse %>% select(country=Entity,iso3c=Code,year=Year,frhouse=Total.democracy.score) %>% 
  mutate(iso2c =countrycode::countrycode(sourcevar = iso3c,origin = "iso3c",destination = "iso2c")) %>% 
  mutate(yr2 = substr(year, 3, 4)) %>% 
  filter(iso2c %in% datos_merge$iso2c)
  
datos_merge<- 
left_join(x = datos_merge,y = wid_data[,c("iso2c","yr2","wid_gini_disp")],
          by =c("iso2c","yr2"))

datos_merge<- 
left_join(x = datos_merge,y = frhouse[,c("iso2c","yr2","frhouse")],
          by =c("iso2c","yr2"))

datos_macro <- datos_merge %>%
  mutate(
   cohesion_horizontal,
      cohesion_vertical,
      cohesion_general,
      gini_index,
      wid_gini_disp,  
      pib_per_capita_ppa,
      log_pib_per_capita_ppa,
      percent_pob_migrante,
      indice_v_dem,
      regulatory_quality,
      voice_and_accountability,
      wgi,
     frhouse, 
    edad_c = scale(edad) %>% as.numeric(),
    ola_s = as.numeric(scale(ola, center = TRUE, scale = TRUE)),
   income_decile,
    ola,
    nivel_educ   = forcats::fct_drop(factor(nivel_educ)),
    pos_politica = forcats::fct_drop(factor(pos_politica)),
    sexo         = forcats::fct_drop(factor(sexo)),
    pais         = forcats::fct_drop(factor(pais)),
    country_wave = forcats::fct_drop(factor(country_wave))
  ) %>% 
    select(cohesion_horizontal,
      cohesion_vertical,
      cohesion_general,
      gini_index,wid_gini_disp,
      pib_per_capita_ppa,
      log_pib_per_capita_ppa,
      percent_pob_migrante,
      indice_v_dem,
      regulatory_quality,
      voice_and_accountability,wgi,frhouse,
      income_decile,escolaridad,
         nivel_educ, sexo, edad_c, ola_s,ola, pos_politica,iso2c,
         country_wave, pais, wt)

# dim(datos_macro);dim(na.omit(datos_macro))
datos_macro$yr2<- substr(datos_macro$ola, 3, 4)

df_sum <- datos_macro %>%
  group_by(iso2c, yr2) %>%
  summarise(across(
    c(cohesion_horizontal,
      cohesion_vertical,
      cohesion_general,
      gini_index,wid_gini_disp,
      pib_per_capita_ppa,
      log_pib_per_capita_ppa,
      percent_pob_migrante,
      indice_v_dem,frhouse,
      wgi),
    mean,
    na.rm = TRUE
  )) %>%
  ungroup() 
df_sum <- 
 df_sum %>% 
  group_by(iso2c) %>%
  mutate(across(
    c(cohesion_horizontal,
      cohesion_vertical,
      cohesion_general,
      gini_index,wid_gini_disp,
      pib_per_capita_ppa,
      log_pib_per_capita_ppa,
      percent_pob_migrante,
      indice_v_dem,frhouse,
      wgi),
    mean,
    na.rm = TRUE,
    .names = "mid_{.col}"
  )) %>%
  ungroup()

df_sum$ctyear <- paste0(df_sum$iso2c,df_sum$yr2)
```

##

:::{.notes}
Longitudinal descriptive
:::

```{r}
#| label: fig-cs
#| fig-cap: Evolution of vertical and horizontal cohesion (2004-2023)
#| fig-cap-location: bottom
#| echo: false

library(ggbreak)

load("../../input/proc/micro-macro-merge.rdata")
load("../../input/proc/datos-fit.rdata")

datos_fit <- datos_fit |>
  select(-escolaridad) |> na.omit()

olas <- datos_fit |>
  filter(!pais %in% c("Canada", "United States")) |>
   group_by(ola) |>
  summarise(horizontal_prom = mean(`cohesion_horizontal_ind`, na.rm=T),
            vertical_prom = mean(`cohesion_vertical_ind`, na.rm=T)) |>
  pivot_longer(
    cols = c(horizontal_prom, vertical_prom),
    names_to = "indicador",
    values_to = "promedio"
  ) |>
  mutate(indicador = dplyr::recode(indicador,
                            horizontal_prom = "Horizontal Cohesion",
                            vertical_prom = "Vertical Cohesion"))

 # dif <- datos_fit |>
 #  filter(!pais %in% c("Canada", "United States")) |>
 #  group_by(ola) |>
 #  summarise(
 #    horizontal_prom = mean(cohesion_horizontal_ind, na.rm = TRUE),
 #    vertical_prom   = mean(cohesion_vertical_ind,   na.rm = TRUE),
 #    diferencia_h_v  = horizontal_prom - vertical_prom,
 #    .groups = "drop"
 #  ) |>
 #   summarise(mean(diferencia_h_v))
 # 
 # dif

olas$ola <- factor(olas$ola)
p<- olas |>
  ggplot(aes(x = ola, y = promedio, color = indicador,group = indicador)) +
  geom_line(linewidth = 1) +
  geom_point() +
  scale_y_continuous(limits = c(0,10))+
  labs(x = "Wave", y = "Social cohesion (1-10)", color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")

#plot_cs <- p + scale_y_cut(breaks=c(3.5), which= c(1,2), scales=c(3, 0.5))
#plot_cs
p
```

##

:::{.notes}
Associations
:::

```{r}
#| echo: false
#| fig-cap: "Association between GDP per capita (PPP) and horizontal cohesion. Red line represents the association including Canada and United States."
#| fig-cap-location: bottom
#| label: fig-hor-cor

library(ggrepel)

df_sum_la <-  df_sum %>% filter(!iso2c %in% c("US","CA"))
df_sum <- df_sum %>% filter(!iso2c=="TT")

fig_gdp_h <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE,
              aes(mid_pib_per_capita_ppa, y = mid_cohesion_horizontal),
              color = "red", size = 0.5,fullrange = TRUE) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_pib_per_capita_ppa, y = mid_cohesion_horizontal),
              color = "black") +
  geom_smooth(data = df_sum,
              aes(x = pib_per_capita_ppa,
                  y = cohesion_horizontal,
                  color = iso2c,
                  shape = iso2c),
              method = "lm", se = FALSE,
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_pib_per_capita_ppa,
                 y = mid_cohesion_horizontal,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "GDP per Capita (PPP)", y = " ", title = "") +
  annotate("label",
           x = Inf, y = -Inf,
           hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_pib_per_capita_ppa,
                                    df_sum$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label",
           x = Inf, y = -Inf,
           hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_pib_per_capita_ppa,
                                    df_sum_la$mid_cohesion_horizontal,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)

fig_gdp_h
```

##

```{r}
#| echo: false
#| fig-cap: "Association between GDP per capita (PPP) and vertical cohesion. Red line represents the association including Canada and United States."
#| fig-cap-location: bottom
#| label: fig-ver-cor

fig_gdp_v <-
  ggplot() +
  geom_smooth(data = df_sum, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_pib_per_capita_ppa, y = mid_cohesion_vertical),
              color = "red", size = 0.5) +
  geom_smooth(data = df_sum_la, method = lm, se = FALSE, fullrange = TRUE,
              aes(mid_pib_per_capita_ppa, y = mid_cohesion_vertical),
              color = "black") +
  geom_smooth(data = df_sum, method = "lm", se = FALSE,
              aes(x = pib_per_capita_ppa, y = cohesion_vertical,
                  color = iso2c, shape = iso2c),
              color = "black", size = 0.1) +
  geom_label(data = df_sum,
             aes(x = mid_pib_per_capita_ppa,
                 y = mid_cohesion_vertical,
                 label = iso2c),
             size = 2.5) +
  scale_y_continuous(limits = c(2, 8)) +
  labs(x = "GDP per Capita (PPP)", y = " ", title = "") +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -1,
           label = paste0("r = ",
                          round(cor(df_sum$mid_pib_per_capita_ppa,
                                    df_sum$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "red",
           label.size = 0.25, family = "serif", size = 3.5) +
  annotate("label", x = Inf, y = -Inf, hjust = 1.08, vjust = -3,
           label = paste0("r = ",
                          round(cor(df_sum_la$mid_pib_per_capita_ppa,
                                    df_sum_la$mid_cohesion_vertical,
                                    use = "complete.obs"), 2)),
           fill = "white", color = "black",
           label.size = 0.25, family = "serif", size = 3.5)

fig_gdp_v
```

##

:::{.notes}
models level 1
:::

```{r data-model-fit}
#| echo: false

set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))    
options(scipen=999)
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,ggplot2,haven,ggrepel,gridExtra,grid)  
rm(list=ls())

load("../../input/proc/micro-macro-merge.rdata")

datos_merge <- datos_merge |>
  mutate(across(where(haven::is.labelled), ~ vctrs::vec_data(.)),
         pais= as.factor(pais))

datos_merge$country_wave = do.call(paste, c(datos_merge[c("pais", "ola")], sep = "_"))

wid_data <- haven::read_dta(file = "../../input/proc/wid_data.dta")
wid_data <- wid_data %>% mutate(yr2=substr(year, 3, 4)) %>% rename(iso2c=country)
datos_merge$iso2c<- countrycode::countrycode(sourcevar = datos_merge$pais,origin = "country.name",destination = "iso2c")
wid_data$iso2c <- as.character(wid_data$iso2c)
datos_merge$yr2<- substr(datos_merge$ola, 3, 4)

frhouse <- read.csv("../../input/orig/freedom-score-fh.csv")
frhouse<- 
frhouse %>% select(country=Entity,iso3c=Code,year=Year,frhouse=Total.democracy.score) %>% 
  mutate(iso2c =countrycode::countrycode(sourcevar = iso3c,origin = "iso3c",destination = "iso2c")) %>% 
  mutate(yr2 = substr(year, 3, 4)) %>% 
  filter(iso2c %in% datos_merge$iso2c)
  
datos_merge<- 
left_join(x = datos_merge,y = wid_data[,c("iso2c","yr2","wid_gini_disp")],
          by =c("iso2c","yr2"))

datos_merge<- 
left_join(x = datos_merge,y = frhouse[,c("iso2c","yr2","frhouse")],
          by =c("iso2c","yr2"))


# Separar los efectos
datos_merge <- datos_merge |>
  group_by(pais) |>
 mutate(pib_be = mean(log_pib_per_capita_ppa, na.rm=T),
         # gini_be = mean(gini_index, na.rm=T),
         gini_be = mean(wid_gini_disp, na.rm=T),
         mig_be = mean(percent_pob_migrante, na.rm=T),
         dem_be = mean(indice_v_dem, na.rm=T),
         wgi_be = mean(wgi, na.rm=T),
         fho_be = mean(frhouse, na.rm=T),
         # edu_be = mean(edu_terciaria, na.rm=T)
        ) |>
  ungroup() |>
  mutate(pib_we = log_pib_per_capita_ppa - pib_be,
          # gini_we = gini_index - gini_be,
          gini_we = wid_gini_disp - gini_be,
          mig_we = percent_pob_migrante - mig_be,
          dem_we = indice_v_dem - dem_be,
          wgi_we = wgi- wgi_be,
          fho_we = frhouse- fho_be,
          # edu_we = edu_terciaria-edu_be
         )

# Centrado y limpieza

z <- function(x) as.numeric(scale(x))

datos_fit <- datos_merge %>%
  filter(!pais %in% c("Canada","United States")) %>% 
  mutate(
    # pib_we  = z(pib_we),   gini_we = z(gini_we), wgi_we = z(wgi_we), dem_we = z(dem_we),
    # mig_we  = z(mig_we),   edu_we = z(edu_we),
    # pib_be  = z(pib_be),   gini_be = z(gini_be), wgi_be = z(wgi_be), dem_be = z(dem_be),
    # mig_be  = z(mig_be),   edu_be = z(edu_be),
    edad_c = scale(edad) %>% as.numeric(),
    ola_s = as.numeric(scale(ola, center = TRUE, scale = TRUE)),
    ola,
    nivel_educ   = forcats::fct_drop(factor(nivel_educ)),
    pos_politica = forcats::fct_drop(factor(pos_politica)),
    sexo         = forcats::fct_drop(factor(sexo)),
    pais         = forcats::fct_drop(factor(pais)),
    country_wave = forcats::fct_drop(factor(country_wave)),

    # --- cambiar categoría de referencia ---
    nivel_educ   = forcats::fct_relevel(nivel_educ, "Primary"),   # ejemplo
    pos_politica = forcats::fct_relevel(pos_politica, "Not declared")         # ejemplo
  ) |>
  select(id_row, cohesion_general_ind, cohesion_vertical_ind, cohesion_horizontal_ind,
         nivel_educ, sexo, edad_c, ola_s, pos_politica,ola,
         income_decile,escolaridad,
         pib_we, gini_we, dem_we, wgi_we, mig_we,fho_we,
         pib_be, gini_be, dem_be, wgi_be, mig_be,fho_be, 
         country_wave, pais, wt) 
library(haven)
save(datos_fit, file="../../input/proc/datos-fit.rdata")
```

```{r}
#| echo: false
load("../../input/proc/datos-fit.rdata")
m0_ch = lmer(cohesion_horizontal_ind ~ 1 + (1 | country_wave) + (1 |pais), data=datos_fit, weights=wt)
#icc(m0_ch, by_group=TRUE) # 2.3% y 5.6%
m0_cv = lmer(cohesion_vertical_ind ~ 1 + (1 | country_wave) + (1 |pais), data=datos_fit, weights=wt)
#icc(m0_cv, by_group=TRUE) # 6.3% y 6.3%
m0_cs = lmer(cohesion_general_ind ~ 1 + (1 | country_wave) + (1 |pais), data=datos_fit, weights=wt)
#icc(m0_cs, by_group=TRUE) # 4.9% y 7.5%
save(m0_ch, file="../../output/modelo_nulo_horizontal.rdata")
save(m0_cv, file="../../output/modelo_nulo_vertical.rdata")
save(m0_cs, file= "../../output/modelo_nulo_completo.rdata")
```

```{r}
#| echo: false

isced_labels <- c(
  "Early education/none",
  "Primary",
  "Lower secondary",
  "Upper secondary",
  "Postsecondary non-terciary",
  "Terciary (short-cycle)",
  "Universitary"
)

datos_fit$isced11 <- car::recode(datos_fit$escolaridad, 
"0 = 0;1:6 = 1;7:9 = 2;10:12 = 3;13:14 = 4;15:16 = 5;17:18 = 6")

datos_fit$isced11 <- factor(
  datos_fit$isced11,
  levels = 0:6,
  labels = isced_labels
)
datos_fit$ola <- as.numeric(haven::as_factor(datos_fit$ola))
datos_fit$nivel_educ <- relevel(datos_fit$nivel_educ,ref = "Secondary")

datos_fit <- 
datos_fit %>% 
  select(cohesion_general_ind, cohesion_vertical_ind, cohesion_horizontal_ind,
         nivel_educ, sexo, edad_c, ola_s, pos_politica,ola,
         income_decile,nivel_educ,
         pib_we, gini_we, dem_we, wgi_we, mig_we,fho_we,
         pib_be, gini_be, dem_be, wgi_be, mig_be,fho_be, 
         country_wave, pais, wt) %>% na.omit() %>% 
  filter(!pais %in% c("Canada","United States")) %>% as.data.frame()

micro_h2 <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + nivel_educ + sexo + edad_c + I(edad_c^2) +  ola +  (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
micro_h <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + nivel_educ + sexo + edad_c + I(edad_c^2) + pos_politica + ola +  (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)

micro_v2 <- lmer(cohesion_vertical_ind ~ 1 + income_decile + nivel_educ + sexo + edad_c + I(edad_c^2) +  ola +  (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
micro_v <- lmer(cohesion_vertical_ind ~ 1 + income_decile + nivel_educ + sexo + edad_c + I(edad_c^2) + pos_politica + ola +  (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)

coef_names<- list("(Intercept)"="(Intercept)",
"income_decile" ="Income decile",                  
"nivel_educPrimary" = "Primary",
"nivel_educTertiary" = "Tertiary",
"pos_politicaLeft"="Left",    
"pos_politicaCenter"="Center",  
"pos_politicaRight"="Right",
"ola"="Time",
"sexoMale"="Male (ref.=Female)",            
"edad_c"="Age",              
"I(edad_c^2)"="Age2"
) 
```

```{r}
library(broom.mixed)
library(dplyr)

# Extraer coeficientes (solo efectos fijos)
tidy_h <- tidy(micro_h, effects = "fixed", conf.int = TRUE) %>%
  mutate(model = "Horizontal")

tidy_v <- tidy(micro_v, effects = "fixed", conf.int = TRUE) %>%
  mutate(model = "Vertical")

# Unir
coef_data <- bind_rows(tidy_h, tidy_v)

coef_data <- coef_data %>%
  mutate(term = recode(term, !!!coef_names))

coef_data <- coef_data %>%
  filter(term != "(Intercept)")
```

```{r}
#| echo: false
#| label: fig-coef-individual
#| fig-cap: Multilevel regression for individual level factors and social cohesion
#| fig-cap-location: bottom

ggplot(coef_data, aes(x = estimate, y = term, color = model)) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                 position = position_dodge(width = 0.5),
                 height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    x = "Coefficient estimate",
    y = "",
    color = "Model"
  ) +
  theme_minimal()
```

## {.scrollable}

:::{.notes}
Models level 2
:::

```{r modelo-cohesion-full}
#| cache: true
#| results: asis
load("../../input/proc/datos-fit.rdata")
library(lme4)
library(texreg)
library(dplyr)
library(correlation)

isced_labels <- c(
  "Early education/none",
  "Primary",
  "Lower secondary",
  "Upper secondary",
  "Postsecondary non-terciary",
  "Terciary (short-cycle)",
  "Universitary"
)

datos_fit$isced11 <- car::recode(datos_fit$escolaridad, 
"0 = 0;1:6 = 1;7:9 = 2;10:12 = 3;13:14 = 4;15:16 = 5;17:18 = 6")

datos_fit$isced11 <- factor(
  datos_fit$isced11,
  levels = 0:6,
  labels = isced_labels
)

datos_fit <- 
datos_fit %>% 
  select(cohesion_general_ind, cohesion_vertical_ind, cohesion_horizontal_ind,
         nivel_educ, sexo, edad_c, ola_s, pos_politica,ola,
         income_decile,
         pib_we, gini_we, dem_we, wgi_we, mig_we,fho_we,
         pib_be, gini_be, dem_be, wgi_be, mig_be,fho_be, 
         country_wave, pais, wt) %>% na.omit() %>% 
  filter(!pais %in% c("Canada","United States"))

datos_fit$ola <- as.numeric(haven::as_factor(datos_fit$ola))
datos_fit$nivel_educ <- relevel(datos_fit$nivel_educ,ref = "Secondary")

coef_names <- list(
  ola = "Time",
  gini_be = "Gini (BE)",
  gini_we = "Gini (WE)",
  pib_be = "GDP (BE)",
  pib_we = "GDP (WE)",
  dem_be = "Democracy (BE)",
  dem_we = "Democracy (WE)",
  wgi_be = "Governace (BE)",
  wgi_we = "Governace (WE)",
  mig_be = "Migration (BE)",
  mig_we = "Migration (WE)"
)

micro <- lmer(cohesion_horizontal_ind ~ 1 + income_decile + nivel_educ + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_econ <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we)
macro_econ_polit <- update(macro_econ,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we)
macro_econ_polit_dem <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we+mig_be+mig_we)

h_demo <- list(macro_econ,macro_econ_polit,macro_econ_polit_dem)

micro <- lmer(cohesion_vertical_ind ~ 1 + income_decile+ nivel_educ + sexo + edad_c + I(edad_c^2) + pos_politica + ola + (1 | country_wave) + (1 | pais), data= datos_fit, weights= wt)
macro_econ <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we)
macro_econ_polit <- update(macro_econ,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we)
macro_econ_polit_dem <- update(micro,. ~ . + gini_be+gini_we+pib_be+pib_we+dem_be+dem_we+wgi_be+wgi_we+mig_be+mig_we)

v_demo <- list(macro_econ,macro_econ_polit,macro_econ_polit_dem)

hv_demo<- c(h_demo,v_demo)
# screenreg(hv_demo,digits=3,custom.coef.map = coef_names)
```

```{r}
#| label: tbl-table004
#| results: asis
#| cache: false
#| tbl-cap: Multilevel regression for country level factors and social cohesion
#| tbl-cap-location: bottom
 
knitreg(hv_demo, digits=3,custom.coef.map = coef_names,caption = NULL,
        custom.header = list("Horizontal"=1:3,"Vertical"=4:6)
        )
```

## 

:::{.notes}
Interactions
:::

```{r modelo-cohesion-int}
#| cache: true
#| results: asis
#| eval: false

#Please run this code independently - it takes around 1 hour 
source("../../proc/proc_interactions.R")
# the output saves two objects "hz_ola.RData" and "vt_ola.RData"
```

```{r coefplot}
#| cache: true
#| results: asis
#| eval: true
#| fig-width: 10
#| fig-height: 8 
#| fig-cap: Interactions
library(ggplot2)
library(tidyr)
library(ggtext)

load(file = "../../output/hz_ola.RData") # horizontal cohesion
load(file = "../../output/vt_ola.RData") # vertical cohesion

hz_gini<- broom.mixed::tidy(hz_ola[[1]],conf.int = T)# gini
hz_gdp <- broom.mixed::tidy(hz_ola[[2]],conf.int = T)# gdp 
hz_demo<- broom.mixed::tidy(hz_ola[[3]],conf.int = T)# democracy
hz_gove<- broom.mixed::tidy(hz_ola[[4]],conf.int = T)# governance
hz_migr<- broom.mixed::tidy(hz_ola[[5]],conf.int = T)# migration

data_hz_plot <- 
bind_rows(
hz_gini %>%filter(term %in%c("ola:gini_be","ola:gini_we"))%>%
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE),
hz_gdp  %>%filter(term%in%c("ola:pib_be","ola:pib_we")) %>% 
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE),
hz_demo %>%filter(term%in%c("ola:dem_be","ola:dem_we")) %>%
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE),
hz_gove %>%filter(term%in%c("ola:wgi_be","ola:wgi_we")) %>% 
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE),
hz_migr %>%filter(term%in%c("ola:mig_be","ola:mig_we")) %>% 
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE)
)

data_hz_plot$cohesion <-"Horizontal" 

vt_gini<- broom.mixed::tidy(vt_ola[[1]],conf.int = T)# gini
vt_gdp <- broom.mixed::tidy(vt_ola[[2]],conf.int = T)# gdp
vt_demo<- broom.mixed::tidy(vt_ola[[3]],conf.int = T)# democracy
vt_gove<- broom.mixed::tidy(vt_ola[[4]],conf.int = T)# governance
vt_migr<- broom.mixed::tidy(vt_ola[[5]],conf.int = T)# migration

data_vt_plot <-
bind_rows(
vt_gini %>%filter(term%in%c("ola:gini_be","ola:gini_we"))%>%
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE),
vt_gdp  %>%filter(term%in%c("ola:pib_be","ola:pib_we")) %>%
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE),
vt_demo %>%filter(term%in%c("ola:dem_be","ola:dem_we")) %>%
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE),
vt_gove %>%filter(term%in%c("ola:wgi_be","ola:wgi_we")) %>%
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE),
vt_migr %>%filter(term%in%c("ola:mig_be","ola:mig_we")) %>%
  tidyr::extract(term,into = c("ola", "macro", "effect"),regex = "^([^:]+):([^_]+)_([^_]+)$",remove = FALSE)
)
data_vt_plot$cohesion <-"Vertical" 

data_coes_plot <- bind_rows(data_vt_plot,data_hz_plot)
data_coes_plot$macro<- factor(data_coes_plot$macro,levels = rev(c("gini","pib","dem","wgi","mig")),ordered = T) 

data_coes_plot %>% 
  ggplot( aes(
  x = estimate,
  y = effect,
  shape = macro,
  group = macro
)) + geom_vline(xintercept = 0,
                color = "red",
                size = 1) + geom_errorbarh(
                  aes(xmin = conf.low, xmax = conf.high),
                  height = 0.2,
                  color = "black",
                  size = 0.5,
                  position = position_dodge(width = 0.5)
                ) + geom_point(size = 2, position = position_dodge(width = 0.5)) + labs(
                  # title = "Interaction of country-level factors with wave on horiztontal social cohesion",
                  # subtitle = "lower cohesion ←         → higher cohesion",
                  x = "Coefficient",
                  caption = stringr::str_wrap("*Note*: Multilevel hybrid model regression (95% CIs). Include country-level factor and wave random slopes within country. Each coefficient corresponds to an independent estimate (see supplementary material).",),
                  y = NULL
                ) + scale_x_continuous(limits = c(-1, 3)) +
                    scale_y_discrete(labels=c("BE\n×Wave","WE\n× Wave "))+
                    scale_shape_manual(labels=rev(c("Gini","GDP","Democracy","Governance","Migration")),
                                         values = c(15, 10, 17, 16, 5))+
                  facet_wrap(facets = "cohesion")+
                  theme(
                  panel.grid.minor = element_blank(),
                  plot.title = element_text(face = "bold",size = 13),
                  legend.title = element_blank(),
                  strip.text = element_text(face = "bold"),
                  axis.title = element_text(face = "bold"),
                  axis.title.x = element_text(margin = margin(t = 10), hjust = 0),
                  axis.title.y = element_text(margin = margin(r = 10), hjust = 1),
                  plot.subtitle = element_text(hjust = 0.5),
                  legend.position = "bottom",
                  axis.text.y = element_markdown(hjust = 1, size = 16),
                  plot.caption = element_textbox_simple(hjust = 0,size = 13)
                )

```

## Discusions





:::{.notes}
Para cerrar, solo volver a recalcar la relevancia de este estudio, que con sus limitaciones y con lo que falta por hacer ya muestran resultados prometedores. Hay pocos estudios que se enfocan en comprender la cohesión social desde una perspectiva longitudinal y multinivel, menos para América Latina, y creemos que los hallazgos que esta investigación pueda entregar son importante para aportar, desde los datos, a la discusión académica y política de la cohesión social. 
:::

## References

